Turtlebot SLAM

### 2013-01-21 trunk/Article/Article.tex
Ready except Conclusion

Most room for improvement clearly is to be found in the second Graph SLAM implementation. The TurtleBot used for this research project has to rely on laser range and odometry data only. To extract features
A robot equipped with for instance a colour sensor is much more suited to successfully perform this Graph SLAM method. Coloured objects could serve as landmarks and large parts of the feature detection can be left out.
\section{Conclusion}
\label{sec:conc}
\bibliography{references}
\nocite{*}
\onecolumn
\appendix

>>>>

Most room for improvement clearly is to be found in the second Graph SLAM implementation. The TurtleBot used for this research project has to rely on laser range and odometry data only. Extracting features from laser range data is out the scope of this project. Doing so could dramatically improve the performance the method. 
A robot equipped with for instance a colour sensor is much more suited to successfully perform this Graph SLAM method. Coloured objects could serve as landmarks and large parts of the feature detection could be left out. Implementing a powerful feature-extractor for laser-range data is definitely a possible solution. Applying the method to a robot that provides different kinds of data is the preferred one, though.

\section{Conclusion}
\label{sec:conc}
\bibliography{references}
\nocite{*}
\onecolumn
\appendix
